---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# turfmapper

<!-- badges: start -->
<!-- badges: end -->

The goal of turfmapper is to plot species * time turf maps.

## Installation

You can install `turfmapper` from  [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Between-the-Fjords/turfmapper")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(turfmapper)
library("tidyverse")
data(heath)
heath_long <- heath %>% 
  pivot_longer(cols = matches("^freq\\d+$"), 
               names_to = "subturf", 
               values_to = "presence", 
               names_prefix = "freq", 
               names_ptypes = list(subturf = integer())) %>% 
  filter(presence != "0")#only want presences

#set up subturf grid
grid <- make_grid(ncol = 4)
```

This function will plot the data from one turf over time. 

```{r one_plot, fig.height=10, fig.width = 7}
heath_long %>%
  filter(plot == "10.1.") %>%
  make_turf_plot(
    year = year, species = species, cover = cover, subturf = subturf, 
    title = glue::glue("Site {.$site}: plot {.$plot}"), 
    grid_long = grid)
```

There are a few taxa than need checking here.

See the vignette for plotting multiple turfs. The vignette's source RMD file can be used as a template.
