---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# turfmapper

<!-- badges: start -->
<!-- badges: end -->

The goal of turfmapper is to plot species * time turf maps.

## Installation

You can install `turfmapper` from  [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("Between-the-Fjords/turfmapper")
```
## Example

`turfmapper` is designed for cases when there are cover is recorded at the turf level, and presence-absence at the subturf level. It can also plot data when there are no subturf level data.

```{r example}
#| message: false
library(turfmapper)
library("tidyverse")

data(heath)
heath_long <- heath |>
  pivot_longer(
    cols = matches("^freq\\d+$"),
    names_to = "subturf",
    values_to = "presence",
    names_prefix = "freq",
    names_transform = list(subturf = as.integer)
  ) |>
  filter(presence != "0") # only want presences

# set up subturf grid
grid <- make_grid(ncol = 4)
```

This function will plot the data from one turf over time. 

```{r one_plot, fig.height=10, fig.width = 7}
heath_long |>
  filter(plot == "10.1.") |>
  (\(x){
    make_turf_plot(
      data = x,
      year = year, species = species, cover = cover, subturf = subturf,
      title = glue::glue("Site {x$site}: plot {x$plot}"),
      grid_long = grid
    )
  })()
```

There are a few taxa than need checking here.

See the vignette for plotting multiple turfs.
